The Astropy Project

### 2017-11-26 main.tex

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform 
data analysis and develop software. A large part of this success owes itself to the vibrant 
community of developers and a continuously-growing ecosystem of tools, web services and stable
well-developed packages that enable easier collaboration on software development, easier 
writing and sharing of software documentation and continuous testing and validation of 
software. While the programming language provides support for array representation \& 
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
computing \citep[\package{scipy};][]{numpy}, publication-quality plotting 
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
to use packages are available which can help with tasks that are not astronomy specific but 
might be performed in the course of astronomical research, for example, interfacing with 
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages significantly reducing the barrier to entry for using many such libraries.

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
by individuals who work on the \astropy project in their own personal
time, by individuals or groups contributing to \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.
Different funding models have been proposed for support of \astropy
(e.g., \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.

>>>>

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform 
data analysis and develop software. A large part of this success owes itself to the vibrant 
community of developers and a continuously-growing ecosystem of tools, web services and stable
well-developed packages that enable easier collaboration on software development, easier 
writing and sharing of software documentation and continuous testing and validation of 
software. While the programming language provides support for array representation \& 
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific 
computing \citep[\package{scipy};][]{scipy}, publication-quality plotting 
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high quality and easy 
to use packages are available which can help with tasks that are not astronomy specific but 
might be performed in the course of astronomical research, for example, interfacing with 
databases or statistical inferences. More recently, the development of package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation process for
most packages significantly reducing the barrier to entry for using many such libraries.

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
by individuals who work on the \astropy project in their own personal
time, by individuals or groups contributing to \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.

Different funding models have been proposed for support of \astropy in the future
(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
Different funding models have been proposed for support of \astropy
(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.
